---
title: "Cabbages"
author: "Jovy Gomez"
date: "October 1 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  


$H_0$: There is no difference in the average vitaminC content between c39 and c52.

$H_0$: There is a difference in the VitaminC average between C39 and C52.  

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitc ~ Cultivation method 
VitC is an integer which makes it numerical 
cultivation is a factor which makes it categorical
Use file Num~Cat 


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(VitC~Cult,data=veggy)
```

The boxplot shows that the average levels of VitC is higher when using the cultivation method C52 than when using the cultivation method C39  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
The numerical results shows that the cultivation method C52 has 1.26 times are vitamin c than when using the cultivation method of C.39.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
The P-value is 0.00000003405 this is less than 0.05 so I will reject the null hypothesis 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Is there a difference in average VitC between c39 and c52 cultivation methods?  


$H_0$: There is no difference in the average vitaminC content between c39 and c52. 

$H_0$: There is a difference in the VitaminC average between C39 and C52.  
I reject the null hypothesis because...

The boxplot shows that the average levels of VitC is higher when using the cultivation method C52 than when using the cultivation method C39.  

The numerical results shows that the cultivation method C52 has 1.26 times are vitamin c than when using the cultivation method of C.39.   

The T-Test is the results of the P-value of 0.00000003405 this is less than 0.05 
       
So I will reject the null hypothesis 

I conclude that there is a diffrence in levels of VitaminC when using the diffrent cultivation methods C39 and C52 
